Exp1 - Opt w_max and {A,phi)

### 2018-03-13 voltagebudget/analysis/paper_figures.Rmd
First complete fig draft

# --------------------------------------------------------------------
# Sweep A
exp <- "72"
freqs <- c(8, 12, 20, 30)

@@

# --------------------------------------------------------------------
# Summarize over As 
fig1 %>% 
  group_by(As, freq) %>% 
  summarise(
    V_osc = mean(V_osc), 
    V_comp = mean(V_comp), 
    errors = mean(errors), 
    variances = mean(variances)) -> fig2

@@

```{r, fig.width=1.9, fig.height=1.8}
fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=errors*1e3, y=variances*1e3, color=V_osc*1e3)) +
  geom_point(size=0.05, alpha=.1) +
  scale_color_gradient(low="purple", high="red", name=expression(V[o] (mvolt))) +
  labs(x="Error (ms)", y="Variance (ms)") +
  theme_classic() +
  theme(
    legend.position="bottom", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc*1e3, y=errors*1e3)) +
  geom_point(size=0.05, alpha=1, color="black") + 
  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
  lims(y=c(0, 10)) +
  theme_classic() -> p2

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc*1e3, y=variances*1e3)) +
  geom_point(size=0.05, alpha=1, color="black") + 
  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
  # lims(y=c(0, 10)) +
  theme_classic() -> p3

@@

plot_grid <- rbind(
  c(NA, NA, NA, 4, 4,   4),
  c(NA, NA, NA, 4, 4,   4),
  c(1, 1, 1, 2, 2,   2),
  c(1,  1,  1,  2, 2,   2),
  c(1,  1,  1,  3, 3,   3),
  c(1,  1,  1,  3, 3,   3))#,
  # c(1,  1,  1,  NA, NA, NA))
grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid)
```

@@

```{r, fig.width=2.7, fig.height=2.2}
fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig2, freq==20), 
            aes(x=V_osc/V_comp, y=errors*1e3), 
            color="black", size=0.8) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p1

fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3)) +
  geom_point(size=0.01, alpha=0.01, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig2, freq==20), 
            aes(x=V_osc/V_comp, y=variances*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o]/V[c]), y="Variance (ms)") -> p2

@@

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 16, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=.1, alpha=0.1, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  facet_wrap(~rank, nrow=2) +
  theme_classic() + 
  scale_x_continuous(breaks=c(0, 1, 2)) +
  scale_y_continuous(breaks=c(0, 10)) +
  theme(
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p3

plot_grid <- rbind(
  c(1, 1, 1, 2, 2), 
  c(1, 1, 1, 2, 2), 
  c(1, 1, 1, 2, 2),
  c(1, 1, 1, NA, NA),
  c(3, 3, 3, 3, 3),
  c(3, 3, 3, 3, 3))
grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid, max_N)
```

@@

```{r, fig.width=2.6, fig.height=2}
max_N <- max(fig1$N)

@@

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc*1e3, y=variances*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=2) +
  geom_line(aes(x=V_osc*1e3, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="N spikes") +
  scale_x_continuous(breaks=c(0, 3, 6)) +
  scale_y_continuous(breaks=c(6, 8)) +
  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p2

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 5, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc*1e3, y=errors*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=1) +
  geom_line(aes(x=V_osc*1e3, y=errors_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="N spikes") +
  scale_x_continuous(breaks=c(0, 3, 6)) +
  scale_y_continuous(breaks=c(2, 8)) +
  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="right", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p3

plot_grid <- rbind(
  c(1,  1,  1,  2, 2, 2, 2, 3, 3, 3, 3),
  c(1,  1,  1,  2, 2, 2, 2, 3, 3, 3, 3),
  c(NA, NA, NA, 2, 2, 2, 2, 3, 3, 3, 3),
  c(NA, NA, NA, 2, 2, 2, 2, 3, 3, 3, 3),
  c(NA, NA, NA, 2, 2, 2, 2, 3, 3, 3, 3))
grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
rm(p1, p2, plot_grid, max_N)
```

@@

```{r, fig.width=2.2, fig.height=1.5}
fig1 %>%
  filter(rank == 0) %>% 
  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=freq)) +
  geom_point(size=0.05, alpha=0.6) + 
  labs(x="Error (ms)", y="Variance (ms)") +
  theme_classic() +
  scale_color_gradient(low="grey", high="black") +
  theme(legend.position="right") +
  labs(x="Error (ms)", y="Variance (ms)") -> p1

plot_grid <- rbind(
  c(1))

grid.arrange(p1, layout_matrix=plot_grid)
rm(p1, plot_grid)
```

>>>>

# --------------------------------------------------------------------
# Sweep A
exp <- "77"
freqs <- c(8, 12, 20, 30)

@@

# --------------------------------------------------------------------
# Summarize over As 
fig1 %>% 
  group_by(As, freq) %>% 
  summarise(
    delta_spikes = mean(delta_spikes), 
    V_osc = mean(V_osc), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop), 
    variances = mean(variances)) -> fig2

@@

```{r, fig.width=2.1, fig.height=1.8}
fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=V_osc*1e3)) +
  geom_point(size=0.05, alpha=.4) +
  scale_color_gradient(low="white", high="red", name=expression(V[o] (mvolt))) +
  labs(x="Error (ms)", y="Variance (ms)") +
  theme_classic() +
  theme(
    legend.position="bottom", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc*1e3, y=errors_pop*1e3)) +
  geom_point(size=0.05, alpha=1, color="black") + 
  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
  lims(y=c(0, 10)) +
  theme_classic() -> p2

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc*1e3, y=variances_pop*1e3)) +
  geom_point(size=0.05, alpha=1, color="black") + 
  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
  # lims(y=c(0, 10)) +
  theme_classic() -> p3

@@

plot_grid <- rbind(
  c(NA, NA, NA, NA, 4, 4,   4),
  c(NA, NA, NA, NA, 4, 4,   4),
  c(1,  1,  1,  1, 2, 2,   2),
  c(1,  1,  1,  1, 2, 2,   2),
  c(1,  1,  1,  1, 3, 3,   3),
  c(1,  1,  1,  1, 3, 3,   3))#,
  # c(1,  1,  1,  NA, NA, NA))
grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid)
```

@@

```{r, fig.width=2.7, fig.height=2.2}
fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors*1e3), 
            color="black", size=0.8) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p1

fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3)) +
  geom_point(size=0.01, alpha=0.01, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=variances*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o]/V[c]), y="Variance (ms)") -> p2

@@

fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 18, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=.1, alpha=0.1, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  facet_wrap(~rank, nrow=3) +
  theme_classic() + 
  scale_x_continuous(breaks=c(0, 1, 2)) +
  scale_y_continuous(breaks=c(0, 10)) +
  theme(
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),s
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p3

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(y=V_osc/V_comp, x=delta_spikes)) +
  geom_jitter(size=0.1, alpha=0.01) + 
  geom_hline(yintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_hline(yintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  labs(y=expression(V[o]/V[c]), x="Spike count") -> p4

plot_grid <- rbind(
  c(1, 1, 1, 2, 2), 
  c(1, 1, 1, 2, 2), 
  c(1, 1, 1, 2, 2),
  c(1, 1, 1, NA, NA),
  c(3, 3, 3, 4, 4),
  c(3, 3, 3, 4, 4),
  c(3, 3, 3, 4, 4))
grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
rm(p1, p2, p3, p4, plot_grid, max_N)
```

@@

```{r, fig.width=3, fig.height=3}
max_N <- max(fig1$N)

@@

fig1 %>% 
  filter(freq==20) %>% 
  # filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc*1e3, y=variances*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=2) +
  geom_line(aes(x=V_osc*1e3, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  scale_x_continuous(breaks=c(0, 4, 8)) +
  scale_y_continuous(breaks=c(8, 12)) +
  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p2

fig1 %>% 
  filter(freq==20) %>% 
  # filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 5, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc*1e3, y=errors*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=1) +
  geom_line(aes(x=V_osc*1e3, y=errors_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  scale_x_continuous(breaks=c(0, 4, 8)) +
  scale_y_continuous(breaks=c(2, 8)) +
  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="right", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p3

# -
M = min(fig1$variances_pop)

fig1 %>% 
  filter(freq==20) %>% 
  mutate(quantile = ntile(V_osc, 10)) %>%
  filter(quantile %in% c(1, 10)) %>% 
  ggplot(aes(x=variances, fill=factor(quantile), group=quantile)) +
  geom_density(alpha=0.6, size=0.2, color="black") +
  geom_vline(xintercept = M, color="black") +
  labs(x="Variance (ms)", y="Density (AU)") +
  scale_fill_manual(
    # values=c("#FFDED3", "#FD0D11"), 
    values=c("grey", "black"),
    name=expression("Deciles V"[o]), 
    labels=c("0 - 10%", "90 - 100%")) +
  theme_classic() +
  theme(
    legend.position="bottom", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8) ) -> p4

fig1 %>% 
  filter(freq==20) %>% 
  ggplot(aes(x=delta_spikes, y=variances*1e3, color=factor(delta_spikes))) +
  geom_boxplot(outlier.size = NA, size=0.8, show.legend=FALSE)+
  labs(x="Spike count", y="Variance (ms)") +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  theme_classic() +
  theme(legend.position="none") -> p5

plot_grid <- rbind(
  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,   3, 3),
  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,   3, 3),
  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,   3, 3),
  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,   3, 3),
  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,   3, 3),
  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,   3, 3),
  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 5,  NA, NA),
  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 5,  NA, NA),
  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 5,  NA, NA))

grid.arrange(p1, p2, p3, p4, p5, layout_matrix=plot_grid)
rm(p1, p2, p3, p4, plot_grid, max_N, M)
```

@@

```{r, fig.width=2, fig.height=1.7}
fig2 %>% 
  ggplot(aes(x=V_osc*1e3, y=delta_spikes, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o] (mvolt)), y="Spike count") +
  scale_color_gradient(low="gold", high="darkgreen") +
  scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

fig2 %>% 
  ggplot(aes(x=V_osc*1e3, y=errors*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme_classic() +
  scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
  theme(legend.position="none", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p2

fig2 %>% 
  ggplot(aes(x=V_osc*1e3, y=variances*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
  scale_color_gradient(low="gold", high="darkgreen") +
  scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

plot_grid <- rbind(
  c(1, 1, 1, 1, NA, NA),
  c(1, 1, 1, 1, NA, NA),
  c(1, 1, 1, 1, NA, NA),
  c(2, 2, 2, 3, 3, 3),
  c(2, 2, 2, 3, 3, 3),
  c(2, 2, 2, 3, 3, 3))

grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid)
```
